---
title: "longlist: data enrichtment w/ compustat"
---

# remove previous data environment
```{r}
#rm(list=ls())
```


# load packages
```{r}
library(readxl)
library(tidyr)
library(ggplot2)
library(RPostgres)
library(tidyverse)
library(tictoc)
library(dplyr) 
```


# interface to WRDS database has previously been established 
# connect to WRDS databse 
```{r}
wrds <- dbConnect(Postgres(), 
                  host='wrds-pgdata.wharton.upenn.edu',
                  port=9737,
                  user='sabkatst',
                  password='S!!140140s',
                  sslmode='require',
                  dbname='wrds')

save(wrds, file = "../R_data/wrds.Rda")
```



# import CVC funds longlist
```{r}
longlist_raw <- as_tibble(read_excel("../Data_tables/CVC_longlist.xlsx")) 

longlist_raw$cvc_fund <- toupper(longlist_raw$cvc_fund)
```


# TIDY DATA TO ARRIVE AT SHORTLIST 

# exclude private companies so that only public companies remain 
CORRECT ---- exclude companies that did not make a cvc investment in observation period
# result: shorlist used for sample
```{r}
shortlist_raw <- longlist_raw %>% filter(is.na(private) & is.na(no_invest_period) & is.na(no_patent_activity)) %>%
  select(-private, -no_invest_period, -no_patent_activity, -cvc_fund_2, -cvc_fund_3)

save(shortlist_raw, file = "../R_data/shortlist_raw.Rda")
```



# DATA ENRICHMENT W/ COMPUSTAT

# query 'Compustat North America - Fundamentals Annual' for financial and market information on parent companies using gvkey as identifier
# observation period 2010-2015
```{r}
id_shortlist <- shortlist_raw$gvkey

shortlist_US <- shortlist_raw %>% filter(country == "US")
id_US <- shortlist_US$gvkey

sqlcmd <- paste("SELECT gvkey, conm, datadate, fyear, datafmt, indfmt, fic, curcd, act, lct, sale, sich, xrd
                  FROM compd.funda
                  WHERE fyear BETWEEN '2008' 
                  AND '2015'
                  AND datafmt = 'STD'
                  AND gvkey = '", id_US,"'", sep="")

# LIST OF DATAFRAMES
funda_list_US <- lapply(sqlcmd, function(x) dbGetQuery(wrds, x)) 

# FINAL DATAFRAME
funda_US <- do.call(rbind, funda_list_US)
```



# query 'Compustat Global - Fundamentals Annual' using gvkey as identifier
# observation period 2010-2015 / include 2008 & 2009 for absorptive capacity measure 
```{r}
shortlist_global <- shortlist_raw %>% filter(country != "US")
id_global <- shortlist_global$gvkey

sqlcmd <- paste("SELECT gvkey, conm, datadate, fyear, datafmt, indfmt, fic, curcd, act, lct, sale, sich, xrd
                  FROM compgd.g_funda
                  WHERE fyear BETWEEN '2008' 
                  AND '2015'
                  AND gvkey = '", id_global,"'", sep="")

# LIST OF DATAFRAMES
funda_list_global <- lapply(sqlcmd, function(x) dbGetQuery(wrds, x)) 

# FINAL DATAFRAME
funda_global <- do.call(rbind, funda_list_global)
```


# join US and global Compustat outputs
```{r}
shortlist <- bind_rows(funda_US, funda_global) %>% rename(parent_company = conm, country = fic) %>% arrange(parent_company)
```



# ENRICH SHORTLIST WITH SIC INFORMATION

# query 'Segment NAICS North America' for SIC code industry information on parent companies using gvkey as identifier
```{r}
id_shortlist <- shortlist$gvkey

sqlcmd <- paste("SELECT gvkey, sics, datadate
                FROM comp.seg_naics
                WHERE datadate BETWEEN '2010-01-01' 
                AND '2015-12-31'
                AND stype = 'BUSSEG'
                AND gvkey = '", id_shortlist,"'", sep="")

# LIST OF DATAFRAMES
seg_list <- lapply(sqlcmd, function(x) dbGetQuery(wrds, x)) 

# FINAL DATAFRAME
seg_df <- do.call(rbind, seg_list)
```


# disconnect wrds connection
```{r}
dbDisconnect(wrds)
```



# RESHAPING SIC OUTPUT DATA 
# re-classification of sic codes to 3-digit level
```{r}
seg_df <- seg_df %>% group_by(gvkey, datadate) %>%
  unique() %>%
  mutate(fyear = as.numeric(substr(datadate, 1, 4))) %>%
  mutate(sic = substr(sics, start = 1, stop = 3))
```


# summarize class characteristics for shortlist -> warning: no differentation made between primary and secondary sic codes
```{r}
shortlist_sum <- seg_df %>%
  group_by(sic) %>%
  summarise(parent_companies = n()) %>%
  mutate(rank = dense_rank(desc(parent_companies))) %>%
  arrange(rank) %>%
  mutate(cum_count = cumsum(parent_companies))
```


# change format of seg_df from long to wide
```{r}
# change order of columns
seg_df <- seg_df[,c(1,3,4,5)]
# group by gvkey und date
seg_df_grouped <- seg_df %>%
  dplyr::group_by(gvkey) %>%
 plyr::count(c("gvkey", "datadate"))
# how many SICs do the companies each have?
qplot(seg_df_grouped$freq, geom="histogram", binwidth=1) 
```

## check
```{r}
# order by n descending
arrange(seg_df_grouped,desc(freq))

# max number of SICs
max(seg_df_grouped$freq)
```


# reshape
```{r}
library(plyr)
seg_df <- ddply(seg_df, c("gvkey","datadate"), transform, 
           sic_number = paste0("sic", seq(length(sic))))
detach(package:plyr, unload=TRUE)
```


# check -> should be until 16 sics
```{r}
distinct(seg_df,sic_number)
```


# reshape
```{r}
seg_wide <- seg_df %>% spread(sic_number, sic) 
```



# JOIN INFO FROM SIC CODES WITH FUNDAMENTALS TO ARRIVE AT FINAL SHORTLIST
```{r}
shortlist <- shortlist %>% left_join(seg_wide, by = c("gvkey", "fyear", "datadate")) %>% unique()
```


# tidy df
# assumption: if no primary/secondary sic data is available from Segment database, then historical sic from Fundamentals applies (only primary one)
```{r}
shortlist$sic1 <- ifelse(is.na(shortlist$sic1), str_sub(shortlist$sich, start = 1, end = 3), shortlist$sic1)
```


# save outout
```{r}
save(shortlist, file = "../R_data/shortlist.Rda")
```
