---
title: "Finalise sample"
---

# remove previous data environment
```{r}
rm(list=ls())
```


# load packages
```{r}
library(readxl)
library(tidyr)
library(ggplot2)
library(RPostgres)
library(tidyverse)
library(tictoc)
library(zoo)
library(readxl)
```


```{r}
load(file = "../R_data/shortlist.Rda")
CVC_longlist <- as_tibble(read_excel("../Data_tables/CVC_longlist.xlsx"))
```


# join with CVC longlist again to join CVC fund names again & tidy
```{r}
CVC_longlist$cvc_fund <- toupper(CVC_longlist$cvc_fund)
CVC_longlist <- CVC_longlist %>% select(cvc_fund, parent_company)
shortlist <- shortlist %>% left_join(CVC_longlist,  by = "parent_company") %>% select(fyear, parent_company, cvc_fund, everything(), -datadate, -datafmt)
```


# exclude financial corporate investors identified by Computstat variable indfmt = FS
```{r}
#unique FS companies in sample
fs <- shortlist %>% filter(indfmt == "FS") %>% distinct(parent_company) 

#unique industrial corporate investors identified by Computstat variable indfmt = FS
indl <- shortlist %>% filter(indfmt == "INDL") %>% distinct(parent_company) 

#exclude & tidy
shortlist <- shortlist %>% anti_join(fs, by = "parent_company") %>% select(-indfmt) 
```


# compute R&D intensity & absorptive capacity (past 3-year sum of R&D intensity)
```{r}
width <- 3
shortlist <- shortlist %>% mutate(rxd_intensity = xrd/sale, absorptive_capacity = rollapply(rxd_intensity, width, sum, align = "right", partial=T)) %>% select(-starts_with("sic"), everything())
```


# full data coverage of all variables must be given in at least 2 years of observation period, otherwise exclude from sample
# fyear 2009, 2010 exluded automatically because all absorptive_capacity = 0
```{r}
sample <- shortlist %>% group_by(parent_company) %>% filter(sum(!is.na(absorptive_capacity))>=2 & sum(!is.na(!act))>=2 & sum(!is.na(lct))>=2) %>% filter(fyear >= 2010 & fyear <= 2015)

n_distinct(sample$parent_company)
n_distinct(sample$country)
```

# convert all currencies to USD (conversion factor based on historical mean change rates)
```{r}
currencies <- read_excel(path = "../Data_tables/currency_conversion.xlsx", col_types = c("numeric", "text", "numeric"))

sample <- left_join(sample, currencies, by = c("fyear", "curcd"))

sample$current_assets = sample$act * sample$conversionFactor
sample$current_liabilies = sample$lct * sample$conversionFactor
sample$sales = sample$sale * sample$conversionFactor
sample$rxd = sample$xrd * sample$conversionFactor

# tidy
sample <- sample %>% select(-act, -lct, -sale, -xrd, -rxd_intensity, -curcd, -conversionFactor) %>% select(-starts_with("sic"), everything())
```


# join with patent & year of incorporation data
```{r}
patents <- read.csv2(file = "../Data_tables/patents.csv", stringsAsFactors=F)
sample <- full_join(sample, patents, by = c("fyear", "parent_company")) %>% select(-starts_with("sic"), everything()) 

# tidy
sample$sic1 <- ifelse(is.na(sample$sic1), sample$sich_x, sample$sic1)
sample$cvc_fund <- ifelse(is.na(sample$cvc_fund), sample$cvc_x, sample$cvc_fund)
sample <- sample %>% select(-sich, -sich_x, -cvc_x) 

# save sample to compute diversity variable
save(sample, file = "../R_data/sample.Rda")
```

NEXT
# 1st: RUN PORTFOLIO SKRIPT
# 2nd: RUN DIVERSITY SKRIPT
# 3rd: RUN SKRIPTS TO COMPUTE OTHER VARIABLES

