---
title: "portfolios"
---

# remove previous data environment
```{r}
rm(list=ls())
```


# load packages
```{r}
library(readxl)
library(tidyr)
library(ggplot2)
library(RPostgres)
library(dplyr) 
library(tidyverse)
library(tictoc)
library(stringr)
```


# load sample & function
```{r}
load(file = "../R_data/sample.Rda")
```



# import all cvc deals data
```{r message=FALSE, warning=FALSE}
file.list <- list.files(path="../CVC_raw_data", 
                        pattern='*.csv', full.names = TRUE)

df.list <- lapply(file.list, read_csv2) 

library(plyr)
cvc_data_raw <- rbind.fill(df.list) %>% dplyr::select(-1,-2, - 8) %>% 
  dplyr::rename(cvc_fund = 'Acquiror name', target_name = "Target name", target_country = "Target country code")

detach(package:plyr, unload=TRUE)

save(cvc_data_raw, file = "../R_data/cvc_data_raw.Rda")


uniquecvcfunds <- cvc_data_raw %>% distinct(cvc_fund)
```



# create fyear & separate sic codes into separate columns
# dplyr::filter deals data for observation period (2008-2016)
```{r}
cvc_data <- cvc_data_raw %>% 
  mutate(fyear = str_sub(`Completed date`, start = -4)) %>% 
  select(-"Completed date") %>% 
  select(fyear, everything()) %>%
  dplyr::filter(fyear >= 2007 & fyear <= 2015) %>% 
  separate(`Target US SIC code(s)`, c("sic1", "sic2", "sic3", "sic4", "sic5", "sic6", "sic7", "sic8", "sic9", "sic10", "sic11", "sic12", "sic13", "sic14", "sic15", "sic16"), sep = " / ", remove = FALSE, extra = "warn")  %>% 
  select(- "Target US SIC code(s)")

# convert fyear to numeric
cvc_data$fyear <- as.numeric(cvc_data$fyear)
```



# re-classification of sic codes to 3-digit level
```{r}
cvc_data$sic1 <- str_sub(cvc_data$sic1, 1, end = -2)
cvc_data$sic2 <- str_sub(cvc_data$sic2, 1, end = -2)
cvc_data$sic3 <- str_sub(cvc_data$sic3, 1, end = -2)
cvc_data$sic4 <- str_sub(cvc_data$sic4, 1, end = -2)
cvc_data$sic5 <- str_sub(cvc_data$sic5, 1, end = -2)
cvc_data$sic6 <- str_sub(cvc_data$sic6, 1, end = -2)
cvc_data$sic7 <- str_sub(cvc_data$sic7, 1, end = -2)
cvc_data$sic8 <- str_sub(cvc_data$sic8, 1, end = -2)
cvc_data$sic9 <- str_sub(cvc_data$sic9, 1, end = -2)
cvc_data$sic10 <- str_sub(cvc_data$sic10, 1, end = -2)
cvc_data$sic11 <- str_sub(cvc_data$sic11, 1, end = -2)
cvc_data$sic12 <- str_sub(cvc_data$sic12, 1, end = -2)
cvc_data$sic13 <- str_sub(cvc_data$sic13, 1, end = -2)
cvc_data$sic14 <- str_sub(cvc_data$sic14, 1, end = -2)
cvc_data$sic15 <- str_sub(cvc_data$sic15, 1, end = -2)
cvc_data$sic16 <- str_sub(cvc_data$sic16, 1, end = -2)
```



# CREATE PORTFOLIOS

# determine to which portfolio years cvc investment belongs
# assumption: each target remains in portfolio for 4y on average, if no further round of funding made
# if further funding, then assumption that target remains in portfolio from first invest. year onwards until nth invest. year +4
```{r}
cvc_data$portfolio_year <- NA
cvc_data <- cvc_data %>% select(fyear, portfolio_year, everything())

deals_number <- dim(cvc_data)[1]
cvc_data_copy <- cvc_data
cvc_data <- cvc_data_copy[1,]
cvc_data[] <-  cvc_data[FALSE, ]

tracker <- 1

# run through each deal
for (i in 1:deals_number) {
  
  cvc_temp <- cvc_data_copy[i, ]
  cvc_temp$portfolio_year <- cvc_temp$fyear
  cvc_data[dim(cvc_data)[1]+1,] <- cvc_temp
  
  cvc_temp$portfolio_year <- cvc_temp$fyear+1
  cvc_data[dim(cvc_data)[1]+1,] <- cvc_temp
  
  cvc_temp$portfolio_year <- cvc_temp$fyear+2
  cvc_data[dim(cvc_data)[1]+1,] <- cvc_temp
  
  cvc_temp$portfolio_year <- cvc_temp$fyear+3
  cvc_data[dim(cvc_data)[1]+1,] <- cvc_temp
}



# exlucde duplicated rows which were created in case of multiple rounds of investment
cvc_data <- cvc_data %>% 
  dplyr::filter(!is.na(cvc_fund)) %>% 
  group_by_at(vars(cvc_fund, target_name)) %>% 
  distinct(portfolio_year, .keep_all = TRUE)
```


# exlude portfolio years outside observation period
# group by portfolios in each year per investor
```{r}
portfolios <- cvc_data %>% filter(portfolio_year >= 2007 & portfolio_year <= 2015) %>% group_by_at(vars(portfolio_year, cvc_fund, target_name))
```



```{r}
pct <- function(x) {x/lag(x)}
```


# summary statistics for observation period
```{r}
portfolios_copy <- portfolios %>% 
  ungroup() %>% 
  group_by_at(vars(cvc_fund, portfolio_year)) %>%
  mutate(n = row_number(target_name)) 

# portfolio size per investor per year
p_size <- portfolios_copy %>% 
  dplyr::summarize(p_size = n())

# mean portfolio size per investor
avg_p_size <- p_size %>% 
  summarize(avg = mean(p_size))

# mean portfolio size per year
avg_p_size2 <- p_size %>% group_by(portfolio_year) %>% 
  summarize(avg = mean(p_size)) %>%
  mutate(perc_change = pct((avg))) 

# mean portfolio size for whole sample
avg_p_size3 <- avg_p_size %>% ungroup() %>% summarize(avg = mean(avg))
```



# save outout
```{r}
save(portfolios, file = "../R_data/portfolios.Rda")
```

