---
title: "Acquisitions & Joint Ventures"
---

# remove previous data environment
```{r}
rm(list=ls())
```


```{r}
library(lubridate)
library(readxl)
library(tidyverse)
library(dplyr)
```


# import deals data
```{r}
ma_jv_raw <- read_excel("../Data_tables/MA&JV.xlsx") 
ma_jv <- ma_jv_raw
```


# transform & tidy
```{r}
ma_jv$completed_date <- if_else(is.na(ma_jv$completed_date) == T, ma_jv$assumed_completion_date, ma_jv$completed_date)

ma_jv <- ma_jv %>% mutate(fyear = year(completed_date)) %>% select(-"Deal Number", -completed_date, -assumed_completion_date, -"Acquiror name")
head(ma_jv)
```



# CREATE PORTFOLIOS

# determine to which portfolio years M&A und Joint Venture activities belong
# assumption: each target can be considered an external source of knowledge for 4y on average
```{r}
ma_jv$portfolio_year <- NA
ma_jv <- ma_jv %>% select(fyear, portfolio_year, everything())


deals_number <- dim(ma_jv)[1]
ma_jv_copy <- ma_jv
ma_jv <- ma_jv_copy[1,]
ma_jv[] <-  ma_jv[FALSE, ]

tracker <- 1

# run through each deal
for (i in 1:deals_number) {
  
  ma_jv_temp <- ma_jv_copy[i, ]
  ma_jv_temp$portfolio_year <- ma_jv_temp$fyear
  ma_jv[dim(ma_jv)[1]+1,] <- ma_jv_temp
  
  ma_jv_temp$portfolio_year <- ma_jv_temp$fyear+1
  ma_jv[dim(ma_jv)[1]+1,] <- ma_jv_temp
  
  ma_jv_temp$portfolio_year <- ma_jv_temp$fyear+2
  ma_jv[dim(ma_jv)[1]+1,] <- ma_jv_temp
  
  ma_jv_temp$portfolio_year <- ma_jv_temp$fyear+3
  ma_jv[dim(ma_jv)[1]+1,] <- ma_jv_temp
}

head(ma_jv)


# tidy
ma_jv <- ma_jv %>% filter(!is.na(parent_company) & portfolio_year >= 2010 & portfolio_year <= 2015) %>% mutate(duration = portfolio_year - fyear) 
```


# mutate weightning variable
# assumption: straight-line depreciation because of declining influence as knowledge source / influence in 1st year=100%, in 5th year=0%
```{r}
ma_jv$weight <- NA
ma_jv$weight <- ifelse(ma_jv$duration==0, 1, ifelse(ma_jv$duration==1, 0.75, ifelse(ma_jv$duration==2, 0.5, ifelse(ma_jv$duration==3, 0.25, NA))))
```


# compute depreciated acquisitions count per investor / per year
```{r}
ma <- ma_jv %>% filter(str_detect(deal_type, "Acquisition")) %>% group_by_at(vars("portfolio_year", "parent_company")) 

acquisitions <- ma %>% select(portfolio_year, parent_company, weight) %>% summarize(acquisitions = sum(weight)) %>% rename(fyear=portfolio_year)
save(acquisitions, file = "../R_data/acquisitions.Rda")
```


# compute depreciated joint ventures count per investor / per year
```{r}
jv <- ma_jv %>% filter(str_detect(deal_type, "Joint")) %>% group_by_at(vars("portfolio_year", "parent_company")) 

jointventures <- jv %>% select(portfolio_year, parent_company, weight) %>%  summarize(jointventures = sum(weight)) %>% rename(fyear=portfolio_year)
save(jointventures, file = "../R_data/jointventures.Rda")
```

